Import_Map

### 2024-05-28 Code/Import_MapMireillePro.Rmd
edits to map code

---
title: "Import_MetaData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r load libraries} 
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
library(googledrive)
library(googlesheets4)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)
library(tidyverse)
library("patchwork") # merging plots

@@

```{r set project variables}
Project <- "BalticO2"
#DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisensePigmentsData")

FigPath <- file.path("..", "Output", "Figures")
#FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

@@

@@

```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZ<- (TropicOMZ/SpringOMZ/SummerFull/WinterOMZ)
OMZ                         
```
```{r}
# d=data.frame(x1=c(400, 700), x2=c(400, 700), y1=c(1), y2=c(2), t=c('a'), r=c(1))
# ggplot() + 
# scale_x_continuous(name="x") + 
# scale_y_continuous(name="y") +
# geom_rect(data=d, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2, fill=t), color="black", alpha=0.5, show.legend = F) +
# geom_text(data=d, aes(x=x1+(x2-x1)/2, y=y1+(y2-y1)/2, label=r), size=4) +
#   
#   stat_wl_strip(aes(x = x1), ymin = -Inf, ymax = Inf, alpha = 0.5) +
#   scale_fill_identity() 
```

```{r}
# d=data.frame(x=c(550,700,700, 400, 550, 400), y=c(100,100,200, 100, 100, 200), t=c('a', 'a', 'a', 'b', 'b', 'b'), r=c(1,2,3, 4, 5, 6))
# ggplot() +
#   stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
#   scale_fill_identity() +
# geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
#   scale_y_continuous(breaks=seq(100, 200, by = 50)) +
#   coord_cartesian(ylim = c(100, 200)) 
```

```{r}
# world_coordinatesRainbow <- map_data("world") 
# world_coordinatesRainbow$nm <- c(400, 700)
# 
# ggplot() + 
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = 100, alpha = 0.5, world_coordinatesRainbow) +
#   scale_fill_identity() +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_blank(),
#         axis.title = element_blank(),
#         axis.ticks = element_blank(),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=14),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.76),
#         legend.text = element_text(size=14))

```{r}

# 
# Rainbow<-ggplot() + 
#   geom_rect(data=d4, mapping=aes(xmin=x1, xmax=x2, ymin=y1, ymax=y2), fill = "green", color="green", alpha=0.4) +
#   geom_map(data = world_coordinatesRainbow, map = world_coordinatesRainbow, aes(long, lat, map_id = region), color = "white", fill = "gray50", size = 0.2) +
#   #geom_text(data=data_textA, aes(x=-190, y=80, label=label), size=8, parse=TRUE) +
#   stat_wl_strip(aes(x = nm), ymin = -Inf, ymax = 100, alpha = 0.5, world_coordinatesRainbow) +
#   scale_fill_identity() +
#   theme_bw() +
#   theme(panel.grid.minor = element_blank(),
#         panel.grid.major = element_blank(),
#         axis.text = element_text(size=14),
#         axis.title = element_text(size=18),
#         strip.background = element_rect(fill="white"),
#         strip.text = element_text(size=14),
#         axis.title.y = element_text(margin=margin(r=10)),
#         axis.title.x = element_text(margin=margin(t=10)),
#         #axis.title.x = element_blank(),
#         legend.background = element_rect(fill="transparent"),
#         legend.position = c(0.12,0.76),
#         legend.key.height= unit(0.005, 'cm'),
#         legend.spacing.x = unit(0.01, 'cm'),
#         legend.text = element_text(size=14))
# Rainbow
```

@@

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~MED4'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow

data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface'))
data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterFullRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterFullRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
FullRainbow<- (TropicFullRainbow/SpringFullRainbow/SummerFullRainbow/WinterFullRainbow)
FullRainbow                         
```

```{r}
data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~SS120~~MIT9313'))
data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicOMZRainbow

data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~MIT9313'))
data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerOMZRainbow

data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~MED4~~SS120~~MIT9313'))
data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~MED4~~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringOMZRainbow

data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~MIT9313'))
data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~SS120~~MIT9313'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=480, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterOMZRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
OMZRainbow                         
```

@@

```{r}
#colnames(CultureCatalog)
```

```{r}
# # create data for world coordinates using map_data() function 
# world_coordinates <- map_data("world") 
#   
# # read volcano_eruption data from volcano.csv 
# volcano_eruption <- readr::read_csv("volcano.csv") 
#   
# # create world map using ggplot() function 
# ggplot() + 
# # geom_map() funct 
# ion takes world coordinates as input 
# # to plot world map color parameter determines the 
# # color of borders in map fill parameter determines the 
# # color of fill in map size determines the thickness of 
# # border in map 
#   geom_map( 
#     data = world, map = world, 
#     aes(long, lat, map_id = region), 
#     color = "green", fill= "lightyellow"
#   )+ 
# # geom_point function is used to plot scatter plot on top  
# # of world map 
# geom_point( 
#     data = volcano_eruption, 
#     aes(longitude, latitude, color = primary_volcano_type, 
#         size=population_within_10_km), 
#     alpha = 1 
#   ) + 
#   
# # legend.position as none removes the legend 
# theme(legend.position="none") 
```

>>>>

---
title: "Import_Map"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r load libraries} 
library(tidyverse)
#library(lubridate)
#library(stringr)
library(broom)
#library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(data.table)
# library(googledrive)
# library(googlesheets4)
library(ggspectra)
library(photobiologyWavebands)
library(photobiology)

library("patchwork") # merging plots

@@

```{r set project variables}
Project <- "prochlorococcus_O2"

FigPath <- file.path("..", "Output", "Figures")
#FigRdsPath <- file.path("..", "Output", "FiguresRds")
#TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

@@

```{r create map omz plot, fig.height = 4, fig.width = 6, warning = FALSE}
data_textA <- data.frame(label = c('A'))

@@

```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZ<- (TropicOMZ/SpringOMZ/SummerFull/WinterOMZ)
OMZ                         
```

@@

data_textTropicFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
data_textTropicFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicFullRainbow

data_textSummerFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
data_textSummerFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerFullRainbow

data_textSpringFullRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI'))
data_textSpringFullRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringFullRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringFullRainbow

data_textWinterFullRainbowSurface <- data.frame(label = c('Near~surface'))
data_textWinterFullRainbowDeep <- data.frame(label = c('Deep:~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterFullRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterFullRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterFullRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterFullRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
FullRainbow<- (TropicFullRainbow/SpringFullRainbow/SummerFullRainbow/WinterFullRainbow)
FullRainbow                         
```

```{r}
data_textTropicOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
data_textTropicOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
TropicOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textTropicOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textTropicOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
TropicOMZRainbow

data_textSummerOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLIV'))
data_textSummerOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SummerOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSummerOMZRainbowSurface, aes(x=500, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSummerOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SummerOMZRainbow

data_textSpringOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
data_textSpringOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~HLI~~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
SpringOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textSpringOMZRainbowSurface, aes(x=530, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textSpringOMZRainbowDeep, aes(x=500, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
SpringOMZRainbow

data_textWinterOMZRainbowSurface <- data.frame(label = c('Near~surface:~Clade~LLIV'))
data_textWinterOMZRainbowDeep <- data.frame(label = c('Deep:~Clade~LLII/III~~Clade~LLIV'))
d=data.frame(x=c(400,700,700), y=c(100,100,200), t=c('a', 'a', 'a'), r=c(1,2,3))
WinterOMZRainbow<-ggplot() +
  stat_wl_strip(aes(x = nm), ymin = 100, ymax = 200, alpha = 0.5, world_coordinatesRainbow) +
  scale_fill_identity() +
  geom_polygon(data=d, mapping=aes(x=x, y=y, group=t), fill = "white", show.legend = F) +
  scale_y_continuous(breaks=seq(100, 200, by = 50)) +
  coord_cartesian(ylim = c(80, 220)) +
  geom_text(data=data_textWinterOMZRainbowSurface, aes(x=480, y=210, label=label), size=5, parse=TRUE) +
  geom_text(data=data_textWinterOMZRainbowDeep, aes(x=480, y=90, label=label), size=5, parse=TRUE) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks = element_blank(),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=14),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.76),
        legend.text = element_text(size=14))
WinterOMZRainbow
```
```{r, warning = FALSE, fig.height = 12, fig.width = 6}
OMZRainbow<- (TropicOMZRainbow/SpringOMZRainbow/SummerOMZRainbow/WinterOMZRainbow)
OMZRainbow                         
```

@@
